\chapter{Minimal Lagrangian diffeomorphism}

\section{Harmonic and minimal maps}
In this section we will briefly introduce harmonic and minimal maps, which will prove useful in the proof of the main theorem.\\
For this purpose let $(M,g)$ and $(N,h)$ be Riemannian manifolds. In local coordinates the metric tensors $g$ and $h$ are given by $(g_{\alpha \beta})_{\alpha,\beta = 1,\cdots, m}$ and $(h_{ij})_{i,j= 1,\cdots,n}$. Moreover let $(g^{\alpha \beta}) = (g^{-1})_{\alpha \beta}$ be the inverse metric tensor on $M$ and let $\Gamma^k_{ij}$ be the Christoffel symbols of the Levi Civita connection of $(N,h)$.\\
\begin{definition}
    The \textit{energy density} of a smooth map $f:M \to N$ is defined as
    \begin{equation}
        e(f)(x) := \frac{1}{2} g^{\alpha \beta}(x)h_{ij}(f(x)) \frac{\partial f^i (x)}{\partial x^\alpha}  \frac{\partial f^j (x)}{\partial x^\beta} \ .
    \end{equation}
    The \textit{energy} of $f$ is
    \begin{equation}
        E(f) := \int_M e(f)dM
    \end{equation}
    where $dM = \sqrt{det(g)} dx^1 \wedge \cdots \wedge dx^m$ is the volume form on $M$.
\end{definition}
\begin{observation}
    Intrinsically $e(f)$ is the trace (up to the factor $\frac{1}{2}$) of $f^* h$ with respect to $g$, and therefore its value on $x$ does not depend on the choices of local coordinates.
\end{observation}
\begin{definition}
    A map $f:M\to N$ is \textit{harmonic} if it is a critical point of the energy functional.
\end{definition}
As harmonic maps are critical points of $E$, a direct computation of
\[
    \frac{d}{dt}E(f+ t\varphi) |_{t=0} = 0
\]
shows that harmonic maps are the solutions of
\begin{equation} \label{eq:harmonic}
    \frac{1}{\sqrt{det(g)}} \frac{\partial}{\partial x^\alpha}(\sqrt{det(g)} g^{\alpha\beta} \frac{\partial f^i}{\partial x^\beta}) + g^{\alpha\beta}(x) \Gamma^k_{ij}(f(x)) \frac{\partial f^i}{\partial x^\alpha}  \frac{\partial f^j}{\partial x^\beta} = 0 \ .
\end{equation}
We turn now our attention to the case where $M$ is a compact surface. As a complex manifold $M$ admits complex coordinate $z=x + iy$ which define on the complexified tangent space the vector fields
\[
\frac{\partial}{\partial z} = \frac{1}{2} \Big(\frac{\partial}{\partial x} -i \frac{\partial}{\partial y} \Big) \ , \qquad \frac{\partial}{\partial \overline{z}} = \frac{1}{2} \Big(\frac{\partial}{\partial x} + i \frac{\partial}{\partial y} \Big) ,
\]
and on the complexified cotangent space the 1-forms
\[
dz = dx + idy \ , \qquad d\overline{z} = dx - idy \ .
\]
\begin{definition}
    A Riemannian metric $\langle \cdot , \cdot \rangle$ on a surface $M$ is called $\textit{conformal}$ if in local coordinates it can be written as
    \[
        \rho^2(z) dz d\overline{z}
    \]
    for a positive, real valued function $\rho(z)$. In particular, we have that
    \[
    \begin{split}
        \Big\langle \frac{\partial}{\partial z}, \frac{\partial}{\partial z} \Big\rangle & = 0 = \Big\langle \frac{\partial}{\partial \overline{z}}, \frac{\partial}{\partial \overline{z}} \Big\rangle \ , \\
         \Big\langle \frac{\partial}{\partial z}, \frac{\partial}{\partial \overline{z}} \Big\rangle & = 2 \rho^2(z).
    \end{split}
    \]
\end{definition}
\begin{observation}
    Using real coordinates a conformal metric is written as 
    \[
        \rho^2(z) (dxdx + dydy)
    \]
    and
    \[
    \begin{split}
        \Big\langle \frac{\partial}{\partial x}, \frac{\partial}{\partial x} \Big\rangle & = \rho^2(z) = \Big\langle \frac{\partial}{\partial y}, \frac{\partial}{\partial y} \Big\rangle \ , \\
         \Big\langle \frac{\partial}{\partial x}, \frac{\partial}{\partial y} \Big\rangle & = 0.
    \end{split}
    \]
\end{observation}

\noindent In complex coordinates Equation \ref{eq:harmonic} is written as
\[
    \frac{\partial^2 f^i}{\partial z \partial \overline{z}} + \Gamma^i_{jk} (f(z)) \frac{\partial f^j}{\partial z} \frac{\partial f^k}{\partial \overline{z}} = 0 \qquad \forall i = 1, \cdots, n \ .
\]
In particular whether a map is harmonic depends only on the Riemann surface structure of $M$, and not on the choice of a conformal metric.\\
When $N$ is a surface with complex coordinates $w = u + iv$ in a neighbourhood of $f(z)$ and conformal metric $h(w) = \sigma(w) dw d\overline{w}$, and $f$ is a local deffeomorphism, Equation \ref{eq:harmonic} becomes
\begin{equation} \label{eq:harmonic2}
    \frac{\partial^2 f}{ \partial z   \partial \overline{z}} + \frac{1}{\sigma(f(z))} \frac{\partial \sigma}{ \partial w} \frac{\partial f}{\partial z} \frac{\partial f}{\partial \overline{z}} = 0 \ ,
\end{equation}
where $w(z) = f^1(z) + i f^2(z)$.
\begin{theorem} \label{thm:HQD}
    Let $M$ be a surface and $N$ a Riemannian manifold with metric $\langle \cdot,\cdot \rangle_N$ or $(g_{ij})_{i,j = 1, \cdots , n}$ in local coordinates. If $f:M \to N$ is harmonic, then the \textit{Hopf differential} of $f$
    \[
        \varphi(z) dz^2 = \Big\langle \frac{\partial f}{\partial z},  \frac{\partial f}{\partial z} \Big\rangle_N dz^2
    \]
    is a holomorphic quadratic differential, i.e $\varphi(z)$ is a holomophic function. \\
    If $f$ is a diffeomorphism the converse holds.
\end{theorem}
\begin{proof}
    In local coordinates
    \[
        \varphi(z)dz^2 = g_{ij}(f(z)) \frac{\partial f^i}{\partial z}  \frac{\partial f^j}{\partial z} dz^2. 
    \]
    Differentiating in $\overline{z}$ we have
    \[
    \begin{split}
       \frac{ \partial}{\partial \overline{z}} \Big(g_{ij}(f(z)) \frac{\partial f^i}{\partial z}  \frac{\partial f^j}{\partial z} \Big) & = 2 g_{ij} \frac{\partial^2 f^i}{\partial z \partial \overline{z}} \frac{\partial f^j}{\partial z} + \frac{\partial g_{ij}}{\partial x^k} \frac{\partial f^k}{\partial \overline{z}} \frac{\partial f^i}{\partial z} \frac{\partial f^j}{\partial z} \\
       & = 2 g_{ij} \frac{\partial^2 f^i}{\partial z \partial \overline{z}} \frac{\partial f^j}{\partial z} + \Big(\frac{\partial g_{lj}}{\partial x^k} + \frac{\partial g_{lk}}{\partial x^j} + \frac{\partial g_{jk}}{\partial x^l} \Big) \frac{\partial f^k}{\partial \overline{z}} \frac{\partial f^l}{\partial z} \frac{\partial f^j}{\partial z}  \\
       & = 2 g_{ij} \frac{\partial f^j}{\partial z} \Big( \frac{\partial^2 f^i}{\partial z \partial \overline{z}} + \Gamma^i_{kl}  \frac{\partial f^k}{\partial \overline{z}} \frac{\partial f^l}{\partial z} \Big) \ ,
    \end{split}
    \]
    which is $0$ when $f$ is harmonic.\\
    Let now $N$ be a surface with complex coordinates $w = f^1 + if^2$ in a neighbourhood of $f(z)$ and conformal metric $h(w) = \sigma(w) dw d\overline{w}$. Now $\varphi(z)$ can be written as $\sigma(f(z)) \frac{\partial f}{ \partial z} \frac{\partial \overline{f}}{\partial z}$ and differentiating in $\overline{z}$ we have
    \[
    \begin{split}
        \frac{ \partial}{\partial \overline{z}}\Big(\sigma(f(z)) \frac{\partial f}{ \partial z}  \frac{\partial \overline{f}}{\partial z} \Big) & = 
        \frac{\partial \sigma}{\partial w} \frac{\partial f}{\partial \overline{z}} \frac{\partial f}{ \partial z} \frac{\partial \overline{f}}{\partial z} +
        \frac{\partial \sigma}{\partial \overline{w}} \frac{\partial \overline{f}}{\partial \overline{z}} \frac{\partial f}{ \partial z} \frac{\partial \overline{f}}{\partial z} +
        \sigma(f(z)) \frac{\partial^2 f}{\partial \overline{z} \partial z} \frac{\partial \overline{f}}{\partial z} +
        \sigma(f(z)) \frac{\partial f}{ \partial z} \frac{\partial^2 \overline{f}}{\partial \overline{z} \partial z} \\
        & = \sigma(f(z)) \frac{\partial \overline{f}}{\partial z} \Big( \frac{\partial^2 f}{\partial \overline{z} \partial z} + \frac{1}{\sigma} \frac{\partial \sigma}{\partial w} \frac{\partial f}{\partial \overline{z}} \frac{\partial f}{ \partial z}  \Big) + 
        \sigma(f(z)) \frac{\partial f}{ \partial z} \overline{ \Big(  \frac{\partial^2 f}{\partial \overline{z} \partial z} + \frac{1}{\sigma} \frac{\partial \sigma}{\partial w} \frac{\partial f}{\partial \overline{z}} \frac{\partial f}{ \partial z}  \Big) }  \\
        & = \sigma(f(z)) \frac{\partial \overline{f}}{\partial z} P + \sigma(f(z)) \frac{\partial f}{ \partial z} \overline{P} \ ,
    \end{split}
    \]
    where $P$ is the left hand side of Equation \ref{eq:harmonic2}.\\
    Suppose now that $f$ is a diffeomorphism and that $\varphi$ is holomorphic. We therefore have
    \[
    \frac{ \partial}{\partial \overline{z}}\Big(\sigma(f(z)) \frac{\partial f}{ \partial z}  \frac{\partial \overline{f}}{\partial z} \Big) = 0 \ .
    \]
    If $f$ is not harmonic, $P\neq 0$.
    Since $|P|=|\overline{P}|$ and $\frac{ \partial}{\partial \overline{z}}\varphi = 0 $, we have
    \[
       \Big| \frac{\partial f}{ \partial z} \Big| = \Big| \frac{\partial \overline{f}}{ \partial z} \Big| = \Big| \frac{\partial f}{ \partial \overline{z}} \Big| \ .
    \]
    This implies that the Jacobian of $f$ is singular which contradics the hypothesis, hence $P=0$ and $f$ is harmonic.
\end{proof}
Before moving on and talk about minimal maps we prove the following result on quadratic differential :
\begin{lemma} \label{lem:HQD}
    Given a Riemannian metric $g$ on a surface $S$ and a $(1,1)$-tensor $A$ which is $g$-symmetric, $A$ is traceless if and only if $g(A \cdot, \cdot)$ is the real part of a quadratic differential for the conformal structure of $g$. Moreover the quadratic differential is holomorphic if and only if A is $g$-Codazzi.
\end{lemma}
\begin{proof}
    Take normal conformal coordinates around a point $x$. In this coordinates $g=\delta_{ij}$ and $A = (A_{ij})_{i,j=1,2}$ where $A_{12}=A_{21}$ since $A$ is $g$-symmetric. Then
    \[
        g(A\cdot , \cdot) = A_{11} (dx^1)^2 + 2 A_{12} dx^1 dx^2 + A_{22} (dx^2)^2 \ .
    \]
    Using complex coordinates $z = x^1 + i x^2$ we have
    \[
        (dx^1)^2 = \frac{dz^2 + 2dzd\overline{z} + d\overline{z}^2}{4} \ , \quad (dx^2)^2 = -\frac{dz^2 - 2dzd\overline{z} + d\overline{z}^2}{4} \ , \quad dx^1dx^2 = i \frac{d\overline{z}^2 - dz^2}{4} \ ,
    \]
    and therefore
    \[
        g(A\cdot , \cdot) = \Big( \frac{A_{11} - A_{22}}{4} - i \frac{A_{12}}{2} \Big)dz^2 + \Big( \frac{A_{11} + A_{22}}{4} \Big)dzd\overline{z} +  \Big( \frac{A_{11} - A_{22}}{4} + i \frac{A_{12}}{2} \Big) d\overline{z}^2 \ .
    \]
    So $g(A\cdot , \cdot)$ is the real part of a quadratic differential if and only if $\frac{A_{11} + A_{22}}{4} = 0$ which happens if and only if $A$ is traceless.\\
    Let now $A$ be traceless, $A_{22}=- A_{11}$ and $g(A \cdot, \cdot)$ writes as
    \[
        g(A\cdot , \cdot) = \Big( \frac{A_{11}}{2} - i \frac{A_{12}}{2} \Big)dz^2 +  \Big( \frac{A_{11}}{2} + i \frac{A_{12}}{2} \Big) d\overline{z}^2 = \varphi dz^2 + \overline{\varphi} d \overline{z}^2 \ .
    \]
    Recall that $d^\nabla A = 0$ means that $\nabla_Y (AX) - \nabla_X (AY) - A(\left[X,Y\right]) = 0$ for all $X,Y \in \Gamma(TS)$, which in normal coordinates is
    \begin{equation}
        Y^i X^j \frac{\partial A_{kj}}{\partial x^i} - X^i Y^j \frac{\partial A_{kj}}{\partial x^i} = 0 \ \ \ \text{for} \ k = 1,2 \ ,
    \end{equation}
    since the Christofell symbols are null. Evaluating $d^\nabla A$ on the pairs $(\frac{\partial}{\partial x^i}, \frac{\partial}{\partial x^j})$ we have that $d^\nabla A = 0$ if and only if
    \[
        \frac{\partial A_{11}}{ \partial x^2} = \frac{\partial A_{12}}{ \partial x^1} \ , \qquad \frac{\partial A_{11}}{ \partial x^1} = - \frac{\partial A_{12}}{ \partial x^2} \ ,
    \]
    which happens if and only if $\varphi$ is holomorphic.
\end{proof}

We now turn our attention to minimal maps.
Let $M$ be a Riemannian manifold, $N$ a Riemannian manifold with metric $\langle \cdot, \cdot \rangle$ and $f:M \to N$ a local embedding. Let $\widetilde{\omega}$ be the volume form on $f(M)$, and $\omega$, $e_1, \cdots , e_m$ a volume form and a frame positively oriented orthonormal frame on $M$. Then
\[
\begin{split}
    \text{Vol}(f(M)) & = \int_{f(M)} \widetilde{\omega} = \int_M f^* \omega  = \int_M | f_* e_1 \wedge \cdots \wedge f_* e_m | \omega = \\
    & = \int_M \langle f_* e_1 \wedge \cdots \wedge f_* e_m ,f_* e_1 \wedge \cdots \wedge f_* e_m \rangle ^{\frac{1}{2}} \omega \ ,
\end{split}
\]
where $\langle v_1 \wedge \cdots \wedge v_m , w_1 \wedge \cdots \wedge w_m \rangle = det(\langle v_i,v_j \rangle)$.\\
Let now $F: M \times (-\epsilon, \epsilon) \to N$ be such that $f_t(\cdot) = F(\cdot,t)$ is a local embedding for all $t$, $f_0 = f$ and
\[ supp F:= \overline{ \{ x\in M \ :\ F(x,t) \neq f(x) \ \text{for some} \ t\} }  \]
is a compact subset of $M$. For easier computation suppose that $M$ is a submanifold of $N$ so that $f = id_M$. The variation of volume is then
\[
    \frac{d}{dt} \text{Vol}(f_t(M)) \Big|_{t=0} = \sum_{i=1}^m \int_M \frac{ \langle f_{t*} e_1 \wedge \cdots \wedge \frac{\partial}{\partial t} f_{t*} e_i \wedge \cdots \wedge f_{t*} e_m ,f_{t*} e_1 \wedge \cdots \wedge f_{t*} e_m \rangle }{| f_{t*} e_1 \wedge \cdots \wedge f_{t*} e_m |} \omega
\]
and putting $X =\frac{\partial}{\partial t} f_{t*} |_{t=0} $ we have
\[
\begin{split}
    \frac{d}{dt} \text{Vol}(f_t(M)) \Big|_{t=0} & = \sum_{i=1}^m \int_M \frac{ \langle e_1 \wedge \cdots \wedge \nabla^N_{e_i} X \wedge \cdots \wedge e_m , e_1 \wedge \cdots \wedge e_m \rangle }{| e_1 \wedge \cdots \wedge e_m |} \omega \\
    & = \int_M \langle \nabla^N_{e_i} X, e_i \rangle \ \omega = - \int_M \langle X, \nabla^N_{e_i} e_i \rangle \ \omega \ .
\end{split}
\]
Since the volume in invariant under reparametrization, we can take assume that $X^\top =0$ and therefore
\[
   \frac{d}{dt} \text{Vol}(f_t(M)) \Big|_{t=0}  = - \int_M \langle X^\perp, \nabla^N_{e_i} e_i \rangle \ \omega \ . 
\]
\begin{definition}
    A submanifold $M$ of a Riemannian manifold $N$ is called \textit{minimal} if it is a critical point of the volume functional i.e
    \[
        \frac{d}{dt} \text{Vol}(f_t(M)) \Big|_{t=0}  = 0
    \]
    for all local variations of $M$.\\
    Moreover, we say a map $f:M \to N$ is \textit{minimal} is $f(M)$ is a minimal submanifold of $N$.
\end{definition}
Similarly to the case of codimension one, for every choice of a vector field $\nu$ normal to $M$ one has
\[
    B_\nu : TM \to TM
\]
defined by $B_\nu(X) = (\nabla^N_X \nu)^\top$, and the \textit{mean curvature} of $M$ in the direction $\nu$ is
\[
    H_\nu := \frac{1}{m} tr(B_\nu) \ .
\]
\begin{theorem}
    A submanifold $M$ of a Riemannian manifold $N$ is minimal if and only if the mean curvature of $M$ vanishes for all normal directions.
\end{theorem}
\begin{proof}
    We fix an orthonormal basis $\nu_1 , \cdots, \nu_k$ of $T_x M^\perp$ and write $X^\perp = \xi^j \nu_j$.
    Then
    \[
        -\langle X^\perp , \nabla^N_{e_i} e_i \rangle = \xi^j tr(B_{\nu_j}) = m \cdot \xi^j H_{\nu_j} \ ,
    \]
    and $M$ is therefore minimal if and only if $m \cdot \xi^j H_{\nu_j}$ vanishes for all choices of $\xi^j$, and the claim follows.
\end{proof}

Let now $f:M \to N$ be an isometric immersion. We want to write the condition for the vanishing of the mean curvature, namely
\[
    (\nabla^N_{e_\alpha} e_\beta)^\perp = 0 \qquad \forall \alpha, \beta \ .
\]
Again we can take normal coordinates on $M$, which, at a point, satisfy the following
\[
    \nabla^M_{\frac{\partial}{\partial x^\alpha}}  \frac{\partial}{\partial x^\beta} = 0 \ ,
\]
for all $\alpha, \beta = 1, \cdots, m$, and we can take
\[
    e_\alpha = f_*\Big( \frac{\partial}{\partial x^\alpha} \Big) = \frac{\partial f^i}{\partial x^\alpha} \frac{\partial}{\partial f^i} \ ,
\]
where $(f^1, \cdots, f^n)$ are local coordinates near $f(x)$.
Since $f$ is an isometric immersion we have $f_* \nabla^M_X Y = \nabla^{f(M)}_{f_* X} f_* Y$, and
\[
\begin{split}
    (\nabla^N_{e_i} e_i)^\perp & = \nabla^N_{e_i} e_i = \nabla^N_{\frac{\partial f^i}{\partial x^\alpha} \frac{\partial}{\partial f^i}}  \frac{\partial f^j}{\partial x^\alpha} \frac{\partial}{\partial f^j} = \\
    & = \frac{\partial^2 f^j}{(\partial x^\alpha)^2} \frac{\partial}{\partial f^j} + \frac{\partial f^i}{\partial x^\alpha} \frac{\partial f^k}{\partial x^\alpha} \Gamma^j_{ik} \frac{\partial}{\partial f^j} \ ,
\end{split}
\]
where $\Gamma^j_{ik}$ are the Christoffel symbols of $N$. Therefore we conclude that $f(M)$ has vanishing mean curvature if and only if
\begin{equation}\label{eq:minimal}
    \frac{\partial^2 f^j}{(\partial x^\alpha)^2} + \frac{\partial f^i}{\partial x^\alpha} \frac{\partial f^k}{\partial x^\alpha} \Gamma^j_{ik}  = 0 \ \ \ \text{for} \ j=1, \cdots, n \ .
\end{equation}
In arbitrary coordinates Equation \ref{eq:minimal} is written as
\[
    \frac{1}{\sqrt{det(g)}} \frac{\partial}{\partial x^\alpha}(\sqrt{det(g)} g^{\alpha\beta} \frac{\partial f^j}{\partial x^\beta}) + g^{\alpha\beta}(x) \Gamma^j_{ik}(f(x)) \frac{\partial f^i}{\partial x^\alpha}  \frac{\partial f^k}{\partial x^\beta} = 0  \ \ \ \text{for} \ j=1, \cdots, n \ ,
\]
where $(g_{\alpha \beta})_{\alpha,\beta = 1,\cdots,m}$ is the metric tensor on $M$.
We can therefore conclude that an isometric immersion is minimal if and only if it is harmonic.\\
Now let $M$ be a surface with metric $g$ and $N$ a Riemannian manifold with metric $h$. We say that a map $f:M \to N$ is \textit{conformal} if $f^* h = \lambda g$ where $\lambda$ is some positive function, namely the pull-back of the metric $h$ is \textit{conformal} to $g$. We already observed that the harmonicity of $f:M \to N$ when $M$ is a surface does not depend on the choice of conformal metric, we can therefore observe that an immersion $f:M \to N$ that is conformal and harmonic, is minimal. It suffices to substitute the metric $g$ on $M$ with the conformal metric $f^* h$, making $f$ an isometric immersion, and now the fact that $f$ is harmonic is now equivalent to it being minimal.\\
To summarize we state the following
\begin{theorem}\label{thm:minimal}
    Let $M$ be a surface with metric $g$ and $N$ a Riemmanian manifold. If $f: M \to N$ is a conformal, harmonic immersion then it is minimal.
\end{theorem}

\section{CMC Surfaces}
We now turn back out attention to smoothly embedded spacelike surfaces in globally hyperbolic AdS spacetime. A surface $S$ has \textit{constant mean curvature} (CMC) if the trace of the shape operator $B$ is constant. A \textit{maximal surface} is a surface $S$ whose mean curvature is constantly equal to zero.
\begin{theorem}\label{thm:CMC_foliation}
    Every MGH Anti-de Sitter manifold with compact Cauchy surface admits a maximal surface.
\end{theorem}
The proof of Theorem \ref{thm:CMC_foliation} revolves around the existence of a pair of barriers which implies existence of a maximal surface. A pair of barriers is a pair of surfaces $\Sigma^+$, $\Sigma^-$ with everywhere positive/negative mean curvature, respectively, and such that $\Sigma^+$ is contained in the future of $\Sigma^-$.
To do this one can take convex hull $C$ of a proper achronal meridian $\Lambda$ that defines $M$. This definition makes sense in affine chart, and in this setting it is well defined since $C \subset \Omega(\Lambda)$ which is contained in a Dirichlet domain. Now $\partial C$ is the union of $\Lambda$ and two surfaces $\partial_+ C$, $\partial_- C$ which are convex and concave respectively. Here a set is convex (resp. concave) if it is contained in the future (resp. past) of all its support planes. Convex (resp. concave) surfaces have non-positive (resp. non-negative) mean curvature. The quotient of $\partial_+ C$, $\partial_- C$ do not work as barriers since they are not smooth, but close to them one can find a pair of smooth barriers.
A detailed proof can be found in \cite{barbot2004constant}. One general fact that follows is that a maximal surface is always contained in the convex hull of its border at infinity.\\
Now we want to prove that such maximal surface is also unique. We already know that given two surfaces $S_1, S_2$ in a MGH spacetime $M$, then the border at infinity of $dev(\widetilde{S_1})$ and $dev(\widetilde{S_2})$ coincide in $dev(\widetilde{M})\subset \A^{2,1}$. Therefore, is suffices to prove the uniqueness in $\A^{2,1}$. Moreover, we can take the problem in $\H^{2,1}$, once we choose a lifting of the border of $dev(\widetilde{S_1})$ and $dev(\widetilde{S_2})$.\\
Let therefore $S_1$ and $S_2$ be lifting to $\H^{2,1}$ of two maximal surfaces in a MGH spacetime $(M,g)$, such that $\partial_\infty S_1 = \partial_\infty S_2$, and let $\rho$ be the lifting to $\text{Isom}(\H^{2,1})$ of the holonomy of $(M,g)$. 
\begin{lemma}\label{lem:maxgen}
    The function 
    \[
    \begin{array}{ccc}
        B: S_1 \times S_2 & \to & \R \\
        (x,y) & \to & \langle x,y \rangle_{2,2}
    \end{array}
    \]
    is negative. Moreover, if $S_1 \neq S_2$ there is a pair $(x,y)$ such that $B(x,y) > -1$ and the function $B$ achieves its maximum.
\end{lemma}
\begin{proof}
    By Proposition \ref{prop:invisible1} we know that for any $x\in S_1$ the border at infinity $\partial_\infty  S_1$ is contained in the region $U_x$ defined in Section \ref{sec:reg}. By definition of $U_x$ we have that $\langle x, \cdot \rangle_{2,2}$ is negative on $\partial_\infty S_1$. Since $\partial_\infty S_1 = \partial_\infty S_2$, $S_2$ is included in $Conv(\partial_\infty S_2)= Conv(\partial_\infty S_1)$ and therefore $\langle x, \cdot \rangle_{2,2}$ is negative on $S_2$.\\
    Let now $S_1 \neq S_2$ and let $x$ be a point in $S_1$ which is not in $S_2$. Choose now an identification of $\H^{2,1}$ with $\D \times \mathbb{S}^1$ in which $x = (0,v_1)$ for some $v_1 \in S^1$. Recalling that $S_2$ is obtained as the graph of a function $f:\D \to \mathbb{S}^1$, there is a point in $S_2$ of the form $y=(0,v_2) = (0, f(0))$. Since $x\notin S_2$ we have $v_2 \neq v_1$. Back in the quadric model we have that $x=(0,0,v_1)$ and $y=(0,0,v_2)$, and therefore
    \[
        B(x,y)= \langle x,y \rangle _{2,2} = - \langle v_1, v_2 \rangle _{\mathbb{S}^1} > -1 \ .
    \]
    We now have to prove that $B$ achieves its maximum. Let $(x_n, y_n) \in S_1 \times S_2$  be a maximazing sequence of $B$. Since $\rho$ acts co-compacly on $S_1$ and preserves $B$, we can suppose that $x_n$ is bounded in $S_1$. Up to extracting a subsequence, we can also assume that $x_n$ converges to $x\in S_1$. Assume by contradiction that $y_n$ is unbounded in $S_2$. Then, up to extracting a subsequence, there exists a sequence of real number $\epsilon_n \to 0$ such that $\epsilon_n y_n$ converges to a vector $y\in \partial_\infty S_2$. This implies that $-1 < B(x_n, y_n) < 0$ for $n$ sufficiently large, then $B(x_n, y_n)$ is bounded and we have
    \[
        B(x,y) = \lim_{n\to +\infty} \epsilon_n B(x_n,y_n) = 0 .
    \]
    The vector $y$ is thus in $x^\perp$, so $y$ is not in $U_x$ which by Proposition \ref{prop:invisible1} contains $\partial_\infty S_1 = \partial_\infty S_2$. So $y \notin \partial_\infty S_2$, hence a contradiction.
\end{proof}
We can now prove the uniqueness of the maximal surface:
\begin{theorem} \label{lem:max}
    Given a proper achronal meridian $\Lambda \subset \H^{2,1}$ there is a unique maximal surface $S$ such that $\partial_\infty S = \Lambda$.
\end{theorem}
\begin{proof}
    Let $S_1$, $S_2$ be two different maximal surface. By Lemma \ref{lem:maxgen} there is a point $(x_0,y_0)\in S_1 \times S_2$ where $B$ achieves its maximum and 
    \[
        -1 < \langle x_0,y_0 \rangle_{2,2} < 0 \ .
    \]
    Let $\dot{x}_0 \in T_{x_0}S_1$ and $\dot{y}_0 \in T_{y_0}S_2$, and let $(x(t))_{t\in(-\epsilon, \epsilon)}$ and $(y(t))_{t\in(-\epsilon, \epsilon)}$ be geodesics on $S_1$ and $S_2$ respectively, satisfying $x(0) = x_0$, $x'(0) = \dot{x}_0$ and $y(0) = y_0$, $y'(0) = \dot{y}_0$.
    Since $B(x(t), y_0)$ is maximal at $t=0$, we have $\langle \dot{x}_0,y_0 \rangle_{2,2}$=0. Similarly. we have $\langle x_0, \dot{y}_0 \rangle_{2,2}$=0. We thus have that $T_{x_0}S_1$ and $T_{y_0}S_2$ are orhogonal to both $x_0$ and $y_0$. Since $x_0, y_0 \in \H^{2,1}$ are not  parallel we also have that $T_{x_0}S_1 = T_{y_0}S_2$.\\
    Denote now by $\II_1$ and $\II_2$ the second fundamental form of $S_1$ and $S_2$.
    The orthogonal projection of $x''(0)$ to $T_{x_0} S$ is given by $\II(\dot{x}_0,\dot{x}_0)\nu$, hence we have
    \[
        \II_1(\dot{x}_0,\dot{x}_0)\nu = x''(0) - q_{2,2}(\dot{x}_0) x_0 \ ,
    \]
    and similarly
    \[
        \II_2(\dot{y}_0,\dot{y}_0)\nu = y''(0) - q_{2,2}(\dot{y}_0) y_0 \ . 
    \]
    Then we have
    \[ 
    \begin{split}
        \frac{d^2}{dt^2}\Big|_{t=0} B(x(t),y(t))  = & \ B(x''(0), y_0) + 2B(\dot{x}_0, \dot{y}_0) + B(x_0, y''(0)) \\
         = & \ 2\langle \dot{x}_0, \dot{y}_0 \rangle_{2,2} + (q_{2,2}(\dot{x}_0) + q_{2,2}(\dot{y}_0)) \langle x_0, y_0 \rangle_{2,2} \\
         & + \langle  \II_1(\dot{x}_0,\dot{x}_0)\nu , y_0 \rangle_{2,2} + \langle \II_2(\dot{y}_0,\dot{y}_0)\nu , x_0 \rangle_{2,2}
    \end{split}
    \]
    Our goal now is to find $\dot{x}_0$ and $\dot{y}_0$ such that this second derivative is positive, in contradiction with the fact that $(x_0, y_0)$ is a point of maximum.\\
    Consider the quadratic form $\beta_1 : w \to \langle  \II_1(w,w)\nu , y_0 \rangle_{2,2}$. Since $S_1$ is maximal, $\II_1$ is traceless and so is $\beta_1$. Hence $\beta_1$ has opposite eigenvalues $\lambda, -\lambda$. Similarly $\beta_2 : w \to \langle \II_2(w,w)\nu , x_0 \rangle_{2,2}$ has opposite eigenvalues $\mu,-\mu$. Up to switching $S_1$ and $S_2$ we can suppose $\lambda \geq \mu \geq 0$. Now we can choose $\dot{x}_0$ and $\dot{y}_0$ such that
    \[
        q_{2,2}(\dot{x}_0) = 1 \ , \qquad \beta_1(\dot{x}_0)= \lambda \ , \qquad \dot{y}_0=\dot{x}_0 \ .
    \] 
    Since $\dot{y}_0$ is unitary, $\beta_2(\dot{y}_0) \geq - \mu \geq -\lambda$, and therefore
    \[
    \begin{split}
        \frac{d^2}{dt^2}\Big|_{t=0} B(x(t),y(t)) & = \ 2\langle \dot{x}_0, \dot{y}_0 \rangle_{2,2} + 2\langle x_0, y_0 \rangle_{2,2} + \beta_1(\dot{x}_0) + \beta_2(\dot{y}_0) \\
        & \geq 2\langle x_0, y_0 \rangle_{2,2} + 2 > 0 \ .
    \end{split}
    \]
    This contradics the maximality of $B$ at $(x_0,y_0)$, hence the maximal surface is unique.
\end{proof}
Given now a spacelike immersion $\sigma$, recall by Lemma \ref{lem:tub metric} that
\[
    B_t = (\cos(t) id + \sin(t) B)^{-1}(-\sin(t) id + \cos(t) B) \ .
\]
Let $\lambda(x)$, $\mu(x)$ be the eigenvalues of $B$. By direct computation one finds that
\begin{equation} \label{eq:eigenvalues}
    \lambda_t(x) = \frac{\lambda(x)+\tan(t)}{1- \lambda(x)\tan(t)} \qquad \mu_t(x) = \frac{\mu(x)+\tan(t)}{1- \mu(x)\tan(t)} \ .
\end{equation}
In general one can find a relation between CMC surfaces and constant Gaussian curvature (CGC) surfaces, namely surfaces where $K = -1 - detB$ is constant, see \cite{chen2017constantmeancurvaturefoliation}. Here we show a weaker result which will prove useful in the proof of the main result:
\begin{proposition} \label{prop:cmc to cgc}
    Let $\sigma: S \to\A^{2,1}$ be a maximal surface. Then the normal evolution $\sigma_{t}$ at the time $t= -\pi / 4$ is an immersion of constant Gaussian curvature $K = -2$.
\end{proposition}
\begin{proof}
    Since $\sigma$ determines a maximal surface $\mu(x) = - \lambda(x)$. By Equation \ref{eq:eigenvalues} the eigenvalues of $B_t$ at time $t=-\pi / 4$ are
    \[
        \lambda_{-\frac{\pi}{4}}(x) = \frac{\lambda(x) -1}{1 +\lambda(x)} \qquad \mu_{-\frac{\pi}{4}}(x) = \frac{\mu(x)-1}{1 + \mu(x)} = \frac{\lambda(x) + 1}{-1 + \lambda(x)} \ .
    \]
    The Gaussian curvature at $x$ is therefore given by
    \[
        K_{-\frac{\pi}{4}}(x) = - 1 - \frac{ \lambda^2(x) -1}{ \lambda^2(x) -1 } = -1 -1 = -2 \ .
    \]
\end{proof}

\section{Minimal Lagrangian diffeomorphisms}

\begin{definition}
    Let $h$ and $h'$ be two hyperbolic metrics on the closed surface $S$. A smooth map $f: (S,h) \to (S,h')$ is \textit{minimal Lagrangian} if its graph is a minimal Lagrangian submanifold of $S\times S$ with respect to the product metric $h \oplus h'$ and the symplectic form $\pi_l^*\omega_h - \pi_r^* \omega_{h'}$. 
\end{definition}

\begin{theorem}\label{thm:existence}
    Given a closed surface $\Sigma$ and two hyperbolic metrics $h$, $h'$ on it, there exists a minimal Lagrangian diffeomorphism $f_0 : (\Sigma,h) \to (\Sigma,h')$ isotopic to the identity.
\end{theorem}
\begin{proof}
    Consider the MGH spacetime $M$, with compact Cauchy surface $\Sigma$, whose holonomy $\rho = (\rho_l, \rho_r)$ induces $h$ and $h'$ as quotient metric in $\H^2 / \rho_l(\pi_1 \Sigma)$ and $\H^2 / \rho_r(\pi_1 \Sigma)$. Let now $\Sigma_0$ be a maximal surface in $M$, we want to prove that the associated map $f_0$ is a minimal Lagrangian diffeomorphism.\\
    First we prove that $f_0$ is a diffeomorphism. By Proposition \ref{prop:cmc to cgc}, $\Sigma_0$ is obtained from a surface $\Sigma_1$ of constant Gaussian curvature equal to $-2$ by normal evolution. The right and left projection of the Gauss map are always local diffeomorphism on a surface with curvature everywhere different from $0$, 
    %and by a topological argument the projections of the Gauss map associated to $\Sigma_1$ are diffeomorphisms. Now, recalling that spacelike immersions which differ from one another by the normal evolution have the same image, we have that the projections are diffeomorphism for $\Sigma_0$, and therefore $f_0$ is a diffeomorphism. 
    and, since $\Sigma_1$ is compact, the projections are proper which makes them embeddings, and ebbeddings from a compact surface to a connected surface are diffeomorphisms.
    Now, recalling from Section \ref{sec:gauss map} that spacelike immersions which differ from one another by the normal evolution have the same image, we have that the projections are diffeomorphism for $\Sigma_0$, and therefore $f_0$ is a diffeomorphism.
    Moreover the Lagrangian condition is equivalent to the fact that $f_0$ is area-preserving, and we proved in Section \ref{sec:gauss map} that this is always verified by the image of the Gauss map.\\
    We now want to prove that the Gauss map is harmonic and conformal, which, by Theorem \ref{thm:minimal} implies that it is minimal.\\
    The pull-back metric via the Gauss map is the sum of $\Pi_l^*g_{\H^2}$ and $\Pi_r^*g_{\H^2}$, which, by Proposition \ref{prop:left right pull-back metric}, is given by
    \[
       \Pi_l^*g_{\H^2} + \Pi_r^*g_{\H^2} = 2I + 2I(\mathcal{J}B,\mathcal{J}B) = 2I + 2I(B,B)= 2(I+ \III) \ .
    \]
    Being $B$ traceless, by the Cayley-Hamilton theorem $B^2 + (\text{det}B)id = 0$. Now, using that $B$ is $\I$-symmetric, we have that $\III = -(\text{det}B)I$, showing conformality.\\
    To prove the harmonicity of the Gauss map it suffices to prove that the left and right projection are harmonic. We check the harmonicity of $\Pi_l$, since the proof is the same for $\Pi_r$. To see this we can write the target metric
    \[
        \Pi_l^*g_{\H^2}=I((\text{id}-\mathcal{J}B)\cdot,(\text{id}-\mathcal{J}B)\cdot) = \I(\cdot, \cdot) + \III(\cdot, \cdot) - 2\I(\mathcal{J}B \cdot, \cdot),
    \]
    where we used that $B$ is traceless and therefore $\mathcal{J}B$ is $\I$-symmetric. Moreover $\mathcal{J} B$ is $I$-Codazzi and by Lemma \ref{lem:HQD} $- 2\I(\mathcal{J}B \cdot, \cdot)$ is the real part of the Hopf differential of $\Pi_l$ which is holomorphic since $\mathcal{J}B$ is $I$-Codazzi. Hence, by Theorem \ref{thm:HQD} we have that $\Pi_l$ is harmonic.
\end{proof}

For the uniqueness of the minimal Lagrangian diffeomorphism we need the following:
\begin{lemma} \label{lem:Lagrangian shit}
    Given a minimal Lagrangian diffeomorphism $\Phi : (S,h) \to (S,h')$ there is a $(1,1)$-tensor $b$ that is $h$-symmetric, $\det(b)=1$, $h$-Codazzi and satisfies
    \[
        \Phi^* h' = h(b \cdot, b \cdot) .
    \]
\end{lemma}
\begin{proof}
    One can always find a $b$ that is $h$-symmetric and such that $\Phi^* h' = h(b \cdot, b \cdot)$. Moreover $\det(b)=1$ since $\Phi$ is area preserving. Hence, we just need to prove that $b$ is $h$-Codazzi.\\
    Since $\text{graph}(\Phi)$ is minimal in $(S,h) \times (S,h')$, the inclusion map is harmonic. A map is harmonic if and only if its factors are, therefore, since $\text{graph}(\Phi) \cong S$, we have that $id:(S,g) \to (S,h)$ and $\Phi:(S,g)\to (S,h')$ are harmonic, where $g$ is the metric induced on $\text{graph}(\Phi)$.
    Since the product metric is the sum of the metric tensor on each factor, we have that
    \[
        g = h + \Phi^* h' = h + h(b \cdot, b \cdot) \ .
    \]
    Define now $G = h((id+b)\cdot ,(id+b)\cdot )$ and $B = (id+b)^{-1}(b-id)$.
    $B$ is $G$-symmetric, indeed for $v,w$ tangent vectors we have
    \[
    \begin{split}
        G(B v,w) & = h((id + b) (id + b)^{-1} (b-id) v , (id + b)w) \\
        & = h((b-id) v , (id + b)w) = h((id + b) v , (b-id)w) \\
        & = G(v, B w) \ .
    \end{split}
    \]
    Moreover, since $\text{det}(b)=1$, a direct computation in a basis where $b$ is diagonal shows that $B$ is traceless. 
    Now, since the minimal polynomial of $b$ is $b^2 - tr(b)b + id = 0$, we have that $(id+b)^2=id+2b+b^2 = (2 + tr(b))b$, hence $G$ is conformal to $g$ because
    \[
        G= h((id+b)^2 \cdot, \cdot) = (2+tr(b))h(b \cdot , \cdot) \ ,
    \]
    and
    \[
        g= h + h(b^2 \cdot,\cdot) = tr(b)h(b\cdot, \cdot) \ .
    \]
    Therefore $id: (S,G)\to (S,h)$ is harmonic too.
    Moreover, using that the minimal polynomial of $B$ is $B^2 + \det(B)id=0$ since $B$ is traceless, and that $id-B = 2(id+b)^{-1}$, we can write
    \[
        \frac{h}{4} = G((id-B) \cdot, (id-B) \cdot) = (1-\det(B))G - 2G(B \cdot , \cdot) \ .
    \]
    Hence, by Lemma \ref{thm:HQD} we have that $G(B\cdot, \cdot)$ is the real part of a harmonic quadratic differential and, by Lemma \ref{lem:HQD}, $B$ is $G$-Codazzi. By Proposition \ref{prop:Gaussian curvature} the Levi-Civita connection of $h$ is given by
    \[
        \nabla^h_Y X= (id-B)^{-1} (\nabla^G_Y (id-B)X) \ ,
    \]
    hence
    \[
    \begin{split}
        (d^{\nabla^h} b)(X,Y) & = (id - B)^{-1} (\nabla^G_Y ((id-B) b X) - \nabla^G_X ((id-B) b Y) ) - b \left[ X,Y \right] \\
        & = (id -B)^{-1} (\nabla^G_Y ((id+B) X) -  \nabla^h_X ((id+B) Y) - (id+B) \left[ X,Y \right] ) \\
        & = (id - B)^{-1}(d^{\nabla^G}(id+B))(X,Y) = 0 \ .
    \end{split}
    \]
    where we used that $b = (id - B)^{-1}(id + B)$, so $b$ is $h$-Codazzi.
\end{proof}

We are now ready to prove the uniqueness
\begin{theorem}
    Given a surface $\Sigma$ and two hyperbolic metrics $h, h'$ on it, the minimal Lagrangian diffeomorphism $\Phi : (\Sigma, h) \to (\Sigma, h')$ is unique.
\end{theorem}
\begin{proof}
    Let $b$ be the unique $(1,1)$-tensor associated to $\Phi$ as in Lemma \ref{lem:Lagrangian shit}. We now want to construct a pair $(\I,\II)$ that define a maximal immersion such that the associated map $f_0$ respect $f_0^* h' = h(b \cdot, b \cdot)$.\\
    Let $\I$ be the metric on $\Sigma$ defined by
    \[
        4 \I = h((id + b)\cdot , (id + b)\cdot ) \ ,
    \]
    let $\mathcal{J}$ be the complex structure defined on $\Sigma$ by $\I$ and $B$ the $(1,1)$-tensor defined by
    \[
        \mathcal{J} B = (id + b)^{-1} (b-id) \ .
    \]
    Here $\I$ and $B$ are well-defined at all points since $b$ has positive eigenvalues. Since $\text{det}(b)=1$, a direct computation in a basis where $b$ is diagonal shows that $\text{tr}(\mathcal{J} B) = 0 $, hence $B$ is $\I$-symmetric. Hence we can set $\II = \I (B \cdot, \cdot)$. We can also write $b$ as
    \[
        b = (id - \mathcal{J}B)^{-1} (id+\mathcal{J}B) \ .
    \]  
    We now have to prove that $\I$ and $B$ satisfy the Gauss-Codazzi equations, and that $B$ is traceless.
    $\mathcal{J} B$ is $\I$-symmetric, indeed for $v,w$ tangent vectors we have
    \[
    \begin{split}
        4I(\mathcal{J}B v,w) & = h((id + b) (id + b)^{-1} (b-id) v , (id + b)w) \\
        & = h((b-id) v , (id + b)w) = h((id + b) v , (b-id)w) \\
        & = 4 I (v, \mathcal{J}B w) \ ,
    \end{split}
    \]
    and it follows that $B$ is traceless.\\
    By Proposition \ref{prop:Gaussian curvature} the Levi-Civita connection $\nabla^I$ of $\I$ is
    \[
        \nabla^I_Y X = (id + b)^{-1} \nabla^h_Y ((id+b)X) \ .
    \]
    Since $b$ is $h$-Codazzi, $(b-id)$ is $h$-Codazzi, and therefore
    \[
    \begin{split}
        (d^{\nabla^I} \mathcal{J}B)(X,Y) & = (id + b)^{-1} (\nabla^h_Y ((id+b)\mathcal{J}B X) - \nabla^h_X ((id+b)\mathcal{J}B Y) ) - \mathcal{J}B \left[ X,Y \right] \\
        & = (id + b)^{-1} (\nabla^h_Y ((b-id) X) -  \nabla^h_X ((b-id) Y) - (b-id) \left[ X,Y \right] ) \\
        & = (id + b)^{-1}(d^{\nabla^h}(b-id))(X,Y) = 0 \ .
    \end{split}
    \]
    Now, since $\mathcal{J}\nabla^I_Y(BX) = (\nabla^I_Y \mathcal{J})(BX)$, we have that $d^{\nabla^I} (\mathcal{J}B) = \mathcal{J} d^{\nabla^I} B$, and therefore $B$ is $h$-Codazzi.\\
    A simple computation shows that 
    \begin{equation}\label{eq:roba}
        (id+ \mathcal{J}B) = 2(id +b)^{-1} b  \ , \qquad (id- \mathcal{J}B) = 2(id +b)^{-1} \ ,
    \end{equation}
     hence, by Proposition \ref{prop:Gaussian curvature} the curvature of $I$ is given by
    \[
        K_I = \frac{-1}{\det((id+b)/2)} = -\det(id - \mathcal{J}B) = -1 - \det(B) \ .
    \]
    We have shown that the pair $(\I,\II)$ defines a maximal immersion.
    Let now $f_0$ be the minimal Lagrangian diffeomorphism associated to the pair $(I,\II)$, the $(1,1)$ tensor associated to $f_0$ in Lemma \ref{lem:Lagrangian shit} is clearly $b_{f_0} = (id+\mathcal{J}B)(id-\mathcal{J}B)^{-1} = b$, hence $f_0 = \Phi$. The uniqueness of the maximal surface ensures that any other minimal Lagrangian diffeomorphism $\Phi'$ is equal, via the same construction, to $f_0=\Phi$, hence the uniqueness.
\end{proof}
